---
title: "Study the ways of people knowing about and getting involved in election campaigns"
output: html_notebook
---

In the introduction file, we analyzed the relationship between racial groups and voting preference. In this R notebook, I would like to study the ways of people engaging in election campaigns. I use data of election surveys from American National Election Studies (ANES). The raw data has over thousand columns, and I clean the data by choosing and renaming 6 of them. Here is a sample of my cleaned data.
```{r, echo=false}
library(haven)
anes_dat <-
    read_sav("C:/Columbia University/GR5243/Project1-zx2338/data/anes_timeseries_cdf.sav")
```


```{r, echo=false}
Election_years<-as.character(seq(1952, 2016, 4))

library(tidyverse)
anes_use<-anes_dat%>%
  mutate(
    year=as_factor(VCF0004),
    age=as_factor(VCF0102),
    activity=as_factor(VCF0723a),
    tv=as_factor(VCF0724),
    radio=as_factor(VCF0725),
    read=as_factor(VCF0726)
  )%>%
  filter(year %in% Election_years)

library(data.table)

data.table(anes_use%>%
             select(year, age, activity, tv, radio, read)%>%
             filter(!is.na(activity) & !is.na(tv) & !is.na(radio) & !is.na(read))%>%
             sample_n(30))


anes_use <- anes_use%>%select(year, age, activity, tv, radio, read)
save(anes_use, file="C:/Columbia University/GR5243/Project1-zx2338/output/data_use.RData")
```





# Question 1:Generally, in which way would people like to get involved in election campaigns?
```{r, echo=false}
table(anes_use$activity)[-1]
table(anes_use$tv)[3]
table(anes_use$radio)[3]
table(anes_use$read)[3]

prop<-c((11273+1628+678)/nrow(anes_use%>%select(activity)%>%filter(!is.na(activity))),
        21752/nrow(anes_use%>%select(tv)%>%filter(!is.na(tv))),
        9849/nrow(anes_use%>%select(radio)%>%filter(!is.na(radio))),
        7055/nrow(anes_use%>%select(read)%>%filter(!is.na(read))))
ways<-c("activity", "tv", "radio", "read")
data<-data.frame(prop=prop, ways=ways)

ggplot(data, aes(x=ways, y=prop))+
  geom_bar(stat = "identity")+
  labs(title="In which way would people like to get involved in election campaigns")
```
Ignoring the NA data, I count the number of people for each of the 4 ways and compute the proportions. It should be noticed that the ways of getting involved in election campaigns are not exclusive choices, so the sum of proportions here is more than 1. Not surprisingly, watching television is the most popular way for people to participate in election campaigns. 

The conclusion here is too general. Since the data contains respondents of all age groups and data over 60 years, I would like to see whether the ways that people choose change with their ages and the eras.




# Question 2: How do people of different ages engage in election campaigns in different years?

Let's look at the four ways separately.
```{r, fig.height=20, fig.width=10, echo=FALSE}
load(file="C:/Columbia University/GR5243/Project1-zx2338/output/data_use.RData")
anes_activity_age_year = anes_use %>%
  filter(!is.na(age) & !is.na(year) & !is.na(activity))%>%
  group_by(year, age)%>%
  count(activity)%>%
  group_by(year, age)%>%
  mutate(
    prop=n/sum(n)
  )

ggplot(anes_activity_age_year, aes(x=year, y=prop, fill=activity)) +
  geom_bar(stat="identity")+ 
  facet_wrap(~age, ncol=1) + 
  theme(axis.text.x = element_text(angle = 90))+
  labs(title="How do people of different ages engage in election campaigns in different years")
```
1.The graph above shows that overall, younger people would be more willing to take part in campaign activities. 

2.Also I have an interesting finding here. After 2000, people participate in campaign activities more and more.

```{r, fig.height=20, fig.width=10, echo=FALSE}
anes_tv_age_year = anes_use %>%
  filter(!is.na(age) & !is.na(year) & !is.na(tv))%>%
  group_by(year, age)%>%
  count(tv)%>%
  group_by(year, age)%>%
  mutate(
    prop=n/sum(n)
  )

ggplot(anes_tv_age_year, aes(x=year, y=prop, fill=tv)) +
  geom_bar(stat="identity")+ 
  facet_wrap(~age, ncol=1) + 
  theme(axis.text.x = element_text(angle = 90))+
  labs(title="How do people of different ages engage in election campaigns in different years")
```
1.We can clearly see that people of all age group love to know about election campaigns through television. 

2.Here is an obviously increasing trend between 1952 and 1960. This increase may be closely related to the prevalence of TV at that time.

```{r, fig.height=20, fig.width=10, echo=FALSE}
anes_radio_age_year = anes_use %>%
  filter(!is.na(age) & !is.na(year) & !is.na(radio))%>%
  group_by(year, age)%>%
  count(radio)%>%
  group_by(year, age)%>%
  mutate(
    prop=n/sum(n)
  )

ggplot(anes_radio_age_year, aes(x=year, y=prop, fill=radio)) +
  geom_bar(stat="identity")+ 
  facet_wrap(~age, ncol=1) + 
  theme(axis.text.x = element_text(angle = 90))+
  labs(title="How do people of different ages engage in election campaigns in different years")
```
1.It is surprising to me that the proportion of young people engaging in campaigns through radio is almost same as that of older ones.

2.In 1952, radio was still a popular way for people of all age groups, but the proportion suddenly decreased in 1956. This may also cause by the the prevalence of TV. 

3.The decrease in proportion for the 7th age group is not obvious. They may had get used to listening to radio programs., and it is hard for older people to change their habits.

```{r, fig.height=20, fig.width=10, echo=FALSE}
anes_read_age_year = anes_use %>%
  filter(!is.na(age) & !is.na(year) & !is.na(read))%>%
  group_by(year, age)%>%
  count(read)%>%
  group_by(year, age)%>%
  mutate(
    prop=n/sum(n)
  )

ggplot(anes_read_age_year, aes(x=year, y=prop, fill=read)) +
  geom_bar(stat="identity")+ 
  facet_wrap(~age, ncol=1) + 
  theme(axis.text.x = element_text(angle = 90))+
  labs(title="How do people of different ages engage in election campaigns in different years")
```

1. Younger people are more likely to get involved in election campaigns by reading magazines. 

2. Reading magazines to know about election campaigns has never been a popular way in all age groups.

# Summary
1.In general, watching TV > listening to radio programs > participating in activities > reading magazine.(Here, ">" means "is more popular than")

1.Participating in activities is more popular among younger people, but more and more people are willing to choose this way with year.

2.Watching TV has been the most popular way for people of all ages after the the prevalence of TV.

3.Listening to radio programs was the most popular way for people of all ages, but then was overtaken by watching TV after the the prevalence of TV.

4.Reading magazines is a more popular way among young people, and and it has never been a popular way in all age groups.

